---
title: "Marriage in Toronto"
author: 
  - Xuanle Zhou
thanks: "Code and data are available at: TorontoOpenData"
date: today
date-format: long
abstract: "None"
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)

data <- read_csv(here::here("data/analysis_data/analysis_data.csv"))


```


# Introduction

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

The remainder of this paper is structured as follows. @sec-data....



# Data {#sec-data}

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Marriage Licences Issued Over Time
#| echo: false
data |>
  ggplot(aes(x=date, y=marriage_licenses))+
  geom_point (color = "blue", size = 2)+
  labs(
    title = "Marriage Licences Issued Over Time",
    x = "Date", 
    y = "Number of Marriage Licences")+
  theme_minimal()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)


\newpage


# References


